\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-12 paper/paper.tex
add comparison table
add compare section

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
\usepackage{amsmath}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
\setlength\parskip{1pt}
\include{figures}

@@

%don't print date
\date{}

@@

@@

@@

\section{Attacks and Defenses}
% 1 page

-Fingerprinting Masked site vs Dark decoy application
-Active probing TLS connection
    -Block access unless from registering source IP
        -cite GFW taking over client IPs for active probing of old obfs
    -Verify knowledge of seed (but how to respond when verification fails?)

>>>>

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
\usepackage{amsmath}
\usepackage{wasysym}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
\setlength\parskip{1pt}
\usepackage{graphicx} % http://ctan.org/pkg/graphicx
\usepackage{booktabs} % http://ctan.org/pkg/booktabs
\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
\include{figures}

@@

\date{}

@@

\FigHighLevel

@@

\subsubsection{WebRTC}

Dark Decoys could also pretend to be clients instead of servers. This may
potentially give censors less to block on, as actively probing clients is common
to return few or no open ports. Nonetheless, a censor may be hesitant to block
client-to-client communication, as it could block peer-to-peer applications as
well as many video conferencing protocols. WebRTC is a
natural choice for a client-to-client protocol in censorship circumvention,
and is used in existing censorship circumvention schemes like
Snowflake~\cite{snowflake}. Dark decoy applications could also use WebRTC as the
application protocol, convincing the censor that two clients are communicating.

@@

\section{Discussion}

\subsection{Comparison to Prior Schemes}

Since 2011, there have been several proposed Refraction Networking schemes.
Telex~\cite{telex}, Cirripede~\cite{cirripede} and Decoy
Routing~\cite{curveball} are ``first generation'' protocols with nearly
identical features. These designs require inline flow blocking at the ISP to
allow the station to intercept flows with detected tags and act as the decoy
host for them. However, inline-blocking is difficult for ISPs to deploy, as it
requires special-purpose hardware to be placed inline with production traffic,
introducing risk of failures and outages that may be expensive for the ISP
and potentially violate their contractual obligations (SLAs).

TapDance~\cite{tapdance} solves the issue of inline-blocking by coercing the
decoy into staying silent, and allowing the station to respond instead. However,
as previously described, this trick comes at a cost: the decoy only stays silent
for a short timeout (typically 30-120 seconds), and limits the amount of data
the client can send before it responds. TapDance clients must keep connections
short and repeatedly reconnect to decoys, increasing overhead and potentially
alerting censors with this pattern. Dark Decoys addresses this issue and allows
clients to maintain long-lived connections to the dark decoy.

Rebound~\cite{rebound} and Waterfall~\cite{waterfall} both focus on routing
asymmetries and routing attacks by the censor. Rebound modifies the client's
packets on the way to the decoy, and uses error pages on the decoy site to
reflect data back to the client. Waterfall only observes and modifies the
decoy-to-client traffic, similarly using error pages on the decoy to reflect
communication from the client to the station. These schemes also provide some
resistance to traffic analysis, as they use the real decoy to reflect data to
the user. Thus, the TCP/TLS behavior seen by the censor more closely matches
that of a legitimate decoy connection. However, latency and other packet-timing
characteristics may be observable, and both schemes require some form of inline
flow blocking.

Slitheen~\cite{slitheen} focuses on addressing observability by replacing
data in packets sent by the legitimate decoy. Thus, even the packet timings and
sizes of a Slitheen connection match that of a legitimate decoy connection.
However, Slitheen also requires inline-blocking, and introduces a large overhead
as it has to wait for the subset of data-carrying packets from the decoy that
Slitheen can safely replace. We note that the Slitheen model of mimicry is
compatible with Dark Decoys, as we could use Slitheen as the application
protocol. Despite using a passive tap, our scheme is effectively inline to the
dark decoy (which won't otherwise respond).

Dark Decoys allow a large amount of flexibility compare to previous schemes.
Because we have significant degrees of freedom in choosing the specific
application the dark decoy will mimic or talk, our scheme can combine the best
of existing Refraction Networking protocols to achieve high performance, be easy
to deploy, and
also be resistant to active attacks such as replaying or probing by the censor.
Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
their features, as compared to Dark Decoys.

\TabCompare

\subsection{Attacks and Defenses}
% 1 page

-Fingerprinting Masked site vs Dark decoy application
-Active probing TLS connection
    -Block access unless from registering source IP
        -cite GFW taking over client IPs for active probing of old obfs
    -Verify knowledge of seed (but how to respond when verification fails?)
-ICMP
